My title

### 2023-10-24 outputs/paper/paper.qmd
Update the data part

## Fox News
It contains the county-level election results during the 2020 Federal Election. For each county, it contains the number of votes for the demographic and republican party

>>>>

## Fox News

It contains the county-level election results during the 2020 Federal Election. For each county, it contains the number of votes for the demographic and republican party.

## Mergin the three sources

To predict the COVID death rate across counties with various socio-economic features, I will merge the the five data sets from the above three data sources by the county and state. In the merged data set, each row represent a US county and provides the number of COVID cases and deaths. In addition, it also shows the demographic information such as the total population and voting pattern such as the number of votes for democratic and republican party. To better understand the graph, I will several graphs.
